### 2025-09-25 paper/sec/evaluation.tex
Better RQ1.

\paragraph{RQ1. How robust is the system when provided with incomplete or ambiguous information?}

In real-world authoring tasks, text fragments may omit key criteria (e.g. \textbf{?}) or contain vague
identifiers (e.g. \textbf{?} without further context). We therefore ask how performance degrades when the
specification is underspecified or when multiple interpretations are possible. Here, we distinguish between
two forms of ambiguity: (1) domain-level ambiguity, which reflects genuine uncertainty in the data (e.g. two
models achieving identical scores). (2) specification-level ambiguity, which arises from incomplete or
imprecise descriptions in the query (e.g. missing fields that would otherwise resolve the expression
uniquely).

>>>>

\paragraph{RQ1. Interpretation Accuracy across Linguistic Idioms and Complexity.}

To what extent can LLMs accurately interpret quantitative and semi-quantitative claims in scholarly text as
data queries? We examine performance across a range of linguistic idioms (e.g. averages, percentages, min/max,
ranks, as summarised in Table~\ref{tab:natural-language-forms}) and investigate how accuracy varies with task
complexity, measured (somewhat crudely and approximately) by the number of query sub-expressions (e.g.
retrieval, aggregation, or arithmetic) present in the gold solution.
